---
title: "movie_imdb"
author: "Edwin Lee"
date: "2023-09-20"
output: 
  html_document:
    toc: true
    toc_depth: 1
    toc_float: true
    collapsed: true
    smooth_scroll: true
    theme: journal
    highlight: kate
    df_print: paged
    code_folding: hide
---

```{r load_libraries, include = FALSE}

library(tidyverse)
library(ggplot2)
library(skimr)
library(dplyr)

```

```{r read_file, include = FALSE}

tibble_movies = read_csv('movies_data.csv')

```

# (1) Display top 10 rows of the dataset.

```{r}

head(tibble_movies, 10)

```

# (2) Display last 10 rows in the dataset.

```{r}

tail(tibble_movies, 10)

```

# (3) Find shape of dataset (number of rows and columns).

```{r}

cat('The number of rows in the dataset is: ', nrow(tibble_movies), '\n')
cat('The number of columns in the dataset is: ', ncol(tibble_movies))

```

# (4) Get information about the dataset.

```{r}

glimpse(tibble_movies)

```

# (5) Check missing values in the dataset.

```{r}

#skim_without_charts(tibble_movies)
revenue_na = sum(is.na(tibble_movies$`Revenue (Millions)`))
metascore_na = sum(is.na(tibble_movies$Metascore))
cat('The number of missing values for Revenue column is: ', revenue_na, '\n')
cat('The number of missing values for Metascore column is: ', metascore_na)

```

# (6) Drop all missing values.

```{r}

tibble_movies_2 = tibble_movies %>% 
  drop_na()

revenue_na_2 = sum(is.na(tibble_movies_2$`Revenue (Millions)`))
metascore_na_2 = sum(is.na(tibble_movies_2$Metascore))
cat('The number of missing values for Revenue column is: ', revenue_na_2, '\n')
cat('The number of missing values for Metascore column is: ', metascore_na_2)

```

# (7) Check for duplicate data.

```{r}

duplicated_data = tibble_movies_2 %>% 
  filter(duplicated(.))

duplicated_data

```

# (8) Get overall statistics about dataset.

```{r}

summary(tibble_movies_2)

```

# (9) Title of the movies having runtime over than 180 minutes.

```{r}

movies_over_180 = tibble_movies_2 %>% 
  filter(`Runtime (Minutes)` >= 180) %>% 
  select(Title, `Runtime (Minutes)`)

movies_over_180

```

# (10) In which year there was the highest average voting?

```{r}

votes_per_year_list = tibble_movies_2 %>% 
  group_by(Year) %>% 
  summarize(mean_votes_per_year = mean(Votes)) %>% 
  arrange(-mean_votes_per_year)

votes_per_year_list

```

```{r}

votes_per_year_list$Year = factor(votes_per_year_list$Year)

ggplot(data=votes_per_year_list, aes(x = Year, y = mean_votes_per_year, fill = Year)) +
  geom_col() + 
  labs(title = 'Average votes per year.', x = 'Year', y = 'Votes') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = scales::comma) + 
  guides(fill = FALSE)

```

# (11) In which year there was the highest average revenue?

```{r}

revenue_per_year_list = tibble_movies_2 %>% 
  group_by(Year) %>% 
  summarize(average_revenue_per_year = mean(`Revenue (Millions)`)) %>% 
  arrange(-average_revenue_per_year)

revenue_per_year_list

```

```{r}

revenue_per_year_list$Year = factor(revenue_per_year_list$Year)

ggplot(data=revenue_per_year_list, aes(x = Year, y = average_revenue_per_year, fill = Year)) +
  geom_col() + 
  labs(title = 'Average revenue per year.', x = 'Year', y = 'Revenue') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(labels = scales::comma) +
  guides(fill = FALSE)

```

# (12) Find the average rating for each director.

```{r}

average_rating_director = tibble_movies_2 %>% 
  group_by(Director) %>% 
  summarize(average_rating = mean(Rating)) %>% 
  arrange(-average_rating)

average_rating_director

```

# (13) Display top 10 lengthy movies title and runtime.

```{r}

lengthy_movies_list = tibble_movies_2 %>%
  select(Title, `Runtime (Minutes)`) %>% 
  arrange(-`Runtime (Minutes)`) %>% 
  head(10)

lengthy_movies_list

```

```{r}

ggplot(data=lengthy_movies_list, aes(x = `Runtime (Minutes)`, y = Title, fill = Title)) + 
  geom_col() + 
  labs(title = 'Top 10 longest runtime movies.', x = 'Minutes', y = 'Title movie') + 
  guides(fill = FALSE)

```

# (14) Display number of movies per year.

```{r}

movies_per_year = tibble_movies_2 %>% 
  group_by(Year) %>% 
  summarize(counter = n()) %>% 
  arrange(-counter)
  
movies_per_year

```

# (15) Find the most popular movie title (highest revenue).

```{r}

most_popular_movie = tibble_movies_2 %>% 
  filter(`Revenue (Millions)` == max(`Revenue (Millions)`)) %>% 
  select(Title, `Revenue (Millions)`)
  
most_popular_movie

```

# (16) Find the least movie title (lowest revenue).

```{r}

most_unpopular_movie = tibble_movies_2 %>% 
  filter(`Revenue (Millions)` == min(`Revenue (Millions)`)) %>% 
  select(Title, `Revenue (Millions)`)

most_unpopular_movie

```

# (17) Display de 10 highest rated movie titles and directors.

```{r}

highest_rated_movies = tibble_movies_2 %>% 
  arrange(-Rating) %>% 
  select(Title, Director, Rating) %>% 
  head(10)

highest_rated_movies

```

```{r}

ggplot(data=highest_rated_movies, aes(x = Title, y = Rating, fill = Director)) + 
  geom_col() + 
  labs(title = 'Top 10 highest rated movies.', x = 'Title', y = 'Rating') + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


# (18) Display top 10 highest revenue movie titles.

```{r}

highest_revenue_movies = tibble_movies_2 %>% 
  arrange(-`Revenue (Millions)`) %>% 
  select(Title, `Revenue (Millions)`) %>% 
  head(10)

highest_revenue_movies

```

```{r}

ggplot(data=highest_revenue_movies, aes(x = `Revenue (Millions)`, y = Title, fill = Title)) + 
  geom_col() + 
  labs(title = 'Top 10 highest revenue movies.', x = 'Revenue', y = 'Title') + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  guides(fill = FALSE)

```

# (19) Find average rating of movies per year.

```{r}

average_rating_per_year = tibble_movies_2 %>% 
  group_by(Year) %>% 
  summarize(average_rating = mean(Rating)) %>% 
  arrange(-average_rating)

average_rating_per_year

```

```{r}

average_rating_per_year$Year = factor(average_rating_per_year$Year)

ggplot(data=average_rating_per_year, aes(x = Year, y = average_rating, fill = Year)) + 
  geom_col() + 
  labs(title = 'Average rating of movies per year.', x = 'Year', y = 'Average rating') + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  guides(fill = FALSE)

```

# (20) Does rating affect the revenue?

```{r}

ggplot(data=tibble_movies_2, aes(x = Rating, y = `Revenue (Millions)`))+
  geom_point() +
  labs(x = 'Rating', y = 'Revenue') + 
  ggtitle('Scatterplot Rating vs Revenue') +
  theme_bw()

```

# (21) Classify movies based on ratings (excellent, good and average).

```{r}

tibble_movies_2 = tibble_movies_2 %>% 
  mutate(Category = case_when(
  Rating >= 7 ~ 'Excellent',
  Rating >= 6 ~ 'Good',
  TRUE ~ 'Average'
))

tibble_movies_2

```

# (22) Count number of action movies.

```{r}

action_movies = tibble_movies_2 %>% 
  filter(str_detect(Genre, 'Action')) %>% 
  nrow()

cat('The number of action movies is: ', action_movies)

```

# (23) Find unique values from genre.

```{r}

genres = tibble_movies_2 %>% 
  separate_rows(Genre, sep = ',') %>% 
  distinct(Genre)

genres

```






